Correlations between gender and research topics at three major archaeology conferences

### 2022-02-08 analysis/paper/paper.Rmd
ready to send to editors

```{r, eval=TRUE}

@@

```{r saa-stm-plot}
#| fig.cap = "Point estimates and 95% confidence intervals for the estimated 
#| marginal effect of gender on each topic identified in titles of presentations at
#| 2018 SAA meeting"

@@

```{r eaa-stm-plot}
#| fig.cap = "Point estimates and 95% confidence intervals for the estimated 
#| marginal effect of gender on each topic identified in titles of presentations at
#| 2018 EAA meeting"

@@

```{r caa-stm-plot}
#| fig.cap = "Point estimates and 95% confidence intervals for the estimated 
#| marginal effect of gender on each topic identified in titles of presentations at
#| 2018 CAA meeting"

@@

For the CAA meeting we have `r prettyNum(CAA18_row, big.mark = ",")` presentations, and `r count_gendered_CAA18` (`r perc_gendered_CAA18`%) first-named authors could be classified as either men (n=`r male_count_CAA18`) or women (n=`r female_count_CAA18`). For CAA we generated a total of `r CAA_stm_topic_number` topics, with `r CAA_stm_topic_number_significant_covary` of these showing non-random co-variance with the gender of the first-named presenter (Figure \@ref(fig:eaa-stm-plot)). Three of these topics were associated with men, and three topics associated with women. Topics associated more with women include archives, GIS, geophysics, collaboration, and teaching. Topics associated more with men include environmental and landscape archaeology.

>>>>

```{r, eval=FALSE}

@@

```{r saa-stm-plot}
#| fig.cap = "Point estimates and 95% confidence intervals for the estimated 
#| marginal effect of gender on each topic identified in titles of presentations at 
#|  the 2018 SAA meeting"

@@

```{r eaa-stm-plot}
#| fig.cap = "Point estimates and 95% confidence intervals for the estimated 
#| marginal effect of gender on each topic identified in titles of presentations at 
#|  the 2018 EAA meeting"

@@

```{r caa-stm-plot}
#| fig.cap = "Point estimates and 95% confidence intervals for the estimated 
#| marginal effect of gender on each topic identified in titles of presentations at 
#|  the 2018 CAA meeting"

@@

For the CAA meeting we have `r prettyNum(CAA18_row, big.mark = ",")` presentations, and `r count_gendered_CAA18` (`r perc_gendered_CAA18`%) first-named authors could be classified as either men (n=`r male_count_CAA18`) or women (n=`r female_count_CAA18`). For CAA we generated a total of `r CAA_stm_topic_number` topics, with `r CAA_stm_topic_number_significant_covary` of these showing non-random co-variance with the gender of the first-named presenter (Figure \@ref(fig:caa-stm-plot)). Three of these topics were associated with men, and three topics associated with women. Topics associated more with women include archives, GIS, geophysics, collaboration, and teaching. Topics associated more with men include environmental and landscape archaeology.
